\vspace{1.0cm} \LARGE \bf Revealing the competitive dynamics of influenza viruses through evolutionary cartography

### 2012-11-29 flux.tex
Include authors.

%\usepackage{authblk}
%\renewcommand\Authands{ \& }
%\renewcommand\Authfont{\normalsize \bf}
%\renewcommand\Affilfont{\small \normalfont}

@@

%%% TITLE %%%
\title{\vspace{1.0cm} \LARGE \bf Revealing the competitive dynamics of influenza viruses through evolutionary cartography}
\author{}
\date{}

>>>>

\usepackage{authblk}
\renewcommand\Authands{ \& }
\renewcommand\Authfont{\normalsize \bf}
\renewcommand\Affilfont{\small \normalfont}

@@

%%% TITLE %%%
\title{\vspace{1.0cm} \LARGE \bf Revealing the competitive dynamics of influenza viruses through evolutionary cartography}

\author[1]{Trevor Bedford}
\author[2,3,4]{Marc A. Suchard}
\author[5]{Philippe Lemey}
\author[1]{Gytis Dudas}
\author[6]{Colin Russell}
\author[6,7]{Derek Smith}
\author[1,8]{Andrew Rambaut}

\affil[1]{Institute of Evolutionary Biology, University of Edinburgh, Edinburgh, UK}
\affil[2]{Department of Biomathematics, David Geffen School of Medicine at UCLA, University of California, Los Angeles CA, USA}
\affil[3]{Department of Human Genetics, David Geffen School of Medicine at UCLA, University of California, Los Angeles CA, USA}
\affil[4]{Department of Biostatistics, UCLA School of Public Health, University of California, Los Angeles CA, USA}
\affil[5]{Department of Microbiology and Immunology, Katholieke Universiteit Leuven, Leuven, Belgium}
\affil[6]{Department of Zoology, University of Cambridge, Cambridge, UK.}
\affil[7]{Department of Virology, Erasmus Medical Centre, Rotterdam, Netherlands.}
\affil[8]{Fogarty International Center, National Institutes of Health, Bethesda, MD, USA.}

\date{}
